Enzo: An Adaptive Mesh Refinement Code for Astrophysics

### 2013-01-21 code-tests.tex
adding Orszag Tang test problem

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Representative MHD test}
\label{sec.tests.mhd}
\red{(Dave)}
One representative MHD test.  What's the best/hardest one?

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection{Representative thermal conduction test}
\label{sec.tests.conduct}
\red{(Brian)}
One test for the thermal conduction (maybe 1 for isotropic, 1 for
anisotropic).

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{MHD: Orszag-Tang Vortex}
\label{sec.tests.mhd}
Figure \ref{fig.orszag} shows the Orszag-Tang vortex problem, a typical test
problem for MHD \citep{Orszag79}.  The left panel shows the MHD-CT result, while
the right panel shows the Dedner result.  This test shows that small scale structure
can be generated in MHD from large scale initial perturbations.  
The test begins 
with uniform density, $\rho_0=25/36 \pi$ and pressure, $P_0=5/12 \pi$.  There is
a single rotational mode in the velocity, and two in the magnetic field: 
${\bf v}_0 $ = (-sin(2$\pi$ y) $ \hat{x}$ , sin(2$\pi$ x) $\hat{y}$),
${\bf B}_0$  =  (-sin(2 $\pi$ y) $ \hat{x},$ sin( 4 $\pi$ x )$\hat{y}$).  The
simulation is evolved to t=0.48.  One can see that the structures are accurately
represented as compared to, for instance, \citet{Toth00}, and that the
resolution of shocks is comparable in both methods.

{\emph Dave's note:  I'll probably play around with these results in future
versions.}

\begin{figure}
\begin{center}
\includegraphics[width=0.4\textwidth]{figures/MHDCT_OrszagTang_Density.eps}
\includegraphics[width=0.4\textwidth]{figures/MHDDedner_OrszagTang_Density.eps}
\caption{TANG}
\label{fig.orszag}
\end{center}
\end{figure}

@@
